RationalGRL: A Framework for Argumentation and Goal Modeling

### 2017-10-16 formalframework.tex
Updated formal framework

\subsection{Formal Specification of GRL}
\label{sect:goalmodeling:logicallanguage}

@@

\begin{definition}[General definitions]
\label{def:set-definitions}
Throughout this section, we adopt the convention that variables start with a lowercase letter (e.g, $id, i, j, name, ie, goal$, and sets and constants start with an uppercase letter (e.g., $Type, AND, Goal$).

We define the following sets:
\begin{itemize}
\item $Type = \{Softgoal, Goal, Task, Resource\}$,
\item $Names$ is a finite set of string.
\item $DecompType = \{AND,OR,XOR\}$.
\item $ContribValue = \{Break, Hurt, Some\ nega-$ $tive, Unknown, Some\  positive, Help, Make\},$
\end{itemize}
\end{definition}

@@

\begin{definition}[Notation]
\label{def:notation}
We adopt three conventions simplifying our notation:
\begin{itemize}
\item
We refer to the element of an intention element $ie$ using the dot (".") notation. That is, we may refer to the id, type, name and decomposition type with respectively $ie.id$, $ie.type$, $ie.name$, and $ie.decomptype$.
\item 
We refer to an intentional element with $ie.id=i$ simply by $ie_i$.\footnote{Note that the reference $ie_i$ is never ambiguous in GRL since identifiers for intentional elements are always unique (see Definition~\ref{def:grlmodel}).} For instance, we may refer to the intentional element $ie = (0, Goal, \text{Make profit}, AND)$ with $ie_0$ and write $ie_0.type = Goal$, $ie_0.name = \text{Make profit}$, and $ie_0.decompositiontype = AND$. 
\item
We can also refer to intention elements of a specific type simply by $type_{id}$. For instance, we can abbreviate the element in the previous item with $goal_0$ and write $goal_0.name = \text{Make profit}$, and $goal_0.decomptype = AND$.
\end{itemize}
\end{definition}

\begin{definition}[Actor]
\label{def:actor}
An actor $act \in \mathbb{N}\times Names$ is a relation where $act=(id,name)$ means:
\begin{itemize}
\item $id\in\mathbb{N}$ refers to the unique identifier of the actor, 
\item $name$ refers to a string description of its name.
\end{itemize}

@@

\begin{definition}[Contribution Link]
\label{def:link:contrib}
A \emph{contribution} link: $contrib\in \mathbb{N}\times\mathbb{N}\times\mathbb{N}\times Contribvalue$ is a relation such that $contrib = (i,j,k,value)$ means
\begin{itemize}
\item $i$ is the unique identifier of the link,
\item $j$ is the unique identifier of the IE from which the contribution originates,
\item $k$ is the unique identifier of the IE to which is contributed.
\end{itemize}
Intuitively, $contrib = (i,j,k,value)$ means that $ie_i$ contributes to $ie_j$ with $value$.

@@

\begin{definition}[Decomposition Link]
\label{def:link:decomp}
A \emph{decomposition} link: $decomp\in \mathbb{N}\times\mathbb{N}\times\mathbb{N}$ is a relation such that $decomp = (i,j,k)$ means
\begin{itemize}
\item $i$ is the unique identifier of the link,
\item $j$ is the unique identifier of the decomposing IE,
\item $k$ is the unique identifier of the IE that is being decomposed.
\end{itemize}
Intuitively, $decomp = (i,j,k)$ means that $ie_i$ decomposes $ie_j$.\footnote{Note that the decomposition type is defined on $IE_{k}$, see Definition~\ref{def:ie}.}

@@

\begin{definition}[Dependency Link]
\label{def:link:dependency}
A \emph{dependency} link: $dep\in \mathbb{N}\times\mathbb{N}\times\mathbb{N}$ is a relation such that $dep = (i,j,k)$ means
\begin{itemize}
\item $i$ is the unique identifier of the link,
\item $j$ is the unique identifier of the dependee IE,
\item $k$ is the unique identifier of the dependent IE.
\end{itemize}
Intuitively, $dep = (i,j,k)$ means that $ie_j$ depends on $ie_j$. \todo{Marc}{Sepideh}{Is this correct? For a dependency relation $A\rightarrow B$, who is dependent on who?}

@@

@@

\begin{definition}[GRL Model]
\label{def:grl-model}
A \emph{GRL model} $GRL=(IE, Act, R_{ActIE}, Contr, Decomp, Dep)$ consists of:
\begin{itemize}
\item A set $IE$ of intentional elements (Def.~\ref{def:ie}),
\item A set $Act$ of actors (Def.~\ref{def:actor}),
\item A set $R_{ActIE}$ of Actor-IE relations (Def.~\ref{def:act-ie-relation}),
\item A set $Contr$ of contribution links (Def.~\ref{def:link:contrib}),
\item A set $Decomp$ of decomposition links (Def.~\ref{def:link:decomp}),
\item A set $Dep$ of dependency links (Def.~\ref{def:link:dependency}).
\end{itemize}

Furthermore, the following conditions are satisfied:
\begin{enumerate}
\item ids are globally unique across IEs, Links, and Actors, i.e., let $X,Y\in \{IE,Act, Contr, Decomp, Dep\}$. For all $X_i$ and $Y_j$: if $i=j$ then $X=Y$ and $X_i=Y_j$.
\item All intentional elements of actors exist: $\forall (i,j)\in R_{ActIE}: act_i \in Act \wedge ie_j \in IE$.
\item An intentional element belongs at most to one actor: $\forall ie_i\in IE: |\{(k,i)\in R_{ActIE}\}| \le 1$.
\item Contribution links connect intentional elements: $\forall (i,j,k,value)\in Contrib: \{ie_j,ie_k\}\subseteq IE$.
\item Decomposition links connect intentional elements: $\forall (i,j,k)\in Decomp: \{ie_j,ie_k\}\subseteq IE$.
\item Dependency links connect intentional elements: $\forall (i,j,)\in Dep: \{ie_j,ie_k\}\subseteq IE$.
\end{enumerate}
\end{definition}

@@

\subsection{Formal specification of RationalGRL}

In order to develop a logical framework for RationalGRL, we extend the GRL logical framework of the previous section by adding three elements (see Figure~\ref{fig:rationalgrllegend}):
\begin{itemize}
\item A new element called \emph{generic argument},
\item A new link called \emph{attack link},
\item An labeling of the elements, assigning to each element (an IE, link, or generic argument) the label IN (accepted) or OUT (reject). In the next section we explain how the labeling is computed, but in this section we only provide a formal definition.
\end{itemize}

Furthermore, we also change the representation of IE, links, and actors. In GRL, these elements have a single identifier. However, in RationalGRL, we allow the user to \emph{replace} such elements when answering a critical question with effect REPLACE. Therefore, for each GRL element, we maintain a history, which is a list in which the last element of the list corresponds to the element that ends up in the GRL model.

@@

\begin{definition}[Generic Argument]
\label{def:generic-argument}
A generic argument $arg \in \mathbb{N}\times Names$ is a relation such that $arg=(id, name)$ is an argument with unique identifier $id$ and name $name$. We may refer to the argument with id $i$ simply with $arg_i$. A set of arguments is denoted by $Arg$.
\end{definition}

@@

\begin{definition}[Attack Link]
\label{def:link:attack}
An attack link $att\in \mathbb{N}\times \mathbb{N}$ is a relation such that $att=(i,j)$ means:
\begin{itemize}
\item $i$ is the unique identifier of the element that is performing that attack,
\item $j$ is the unique identifier of the element that is being attacked.
\end{itemize}
Intuitively, $att=(i,j)$ means that element $i$ is attacking element $j$.
\end{definition}

Note that the previous definition did not put any constraint on which elements can be connected with attack links. This is what we make explicit in the definition of a RationalGRL model later.

We next add the the labeling of elements. This labeling determines whether an element is accepted (which means it shows up in the GRL model if it is an IE or a link), or rejected (which means it won't be shown).

\begin{definition}[RationalGRL labeling]
\label{def:labeling}
A RationalGRL labeling function $Lab:\mathcal{N}\rightarrow {in,out}$ that is total on the ids of the RationalGRL elements. This means that $Lab(id)$ is defined for each $ie.id, contr.id, decomp.id, dep.id, arg.id$.
\end{definition}

Finally we add the last part of the RationalGRL extension. We define a list of intentional elements, contribution links, and actors.

\begin{definition}[IE History, Contribution History, Actor History]
\label{def:element-list}
\begin{itemize}
\item An \emph{IE History for element with id $i$}, denoted $\overline{ie}_i=(ie_0,\ldots,ie_n)$, is a list of IEs $ie_0,\ldots,ie_n$ such that $ie_1.id=\ldots=ie_n.id=i$. 
\item An \emph{Actor history for actor with id $j$}, denoted $\overline{act}_j=(actor_0,\ldots,actor_n)$, is a list of actors $actor_0,\ldots,actor_n$ such that $actor_0.id=\ldots=actor_n.id=j$. 
\item A \emph{Contribution history for link with id $k$}, denoted $\overline{contrib}_j=(contrib_0,\ldots,contrib_n)$, is a list of contribution links $contrib_0,\ldots,contrib_n$ such that $contrib_0.id=\ldots=contrib_n.id=k$.
\end{itemize}
If the id in the list is not relevant we may omit the subscript notation, e.g., we may write $\overline{ie}$ instead of $\overline{ie}_i$.

Sets of histories for IEs, actors, and contribution links are denoted with respectively $\overline{IE}$, $\overline{Act}$, and $\overline{Contrib}$.

The last element of a list is called the \emph{head element}.
\end{definition}

Note that we do not require a history for decomposition links or dependency links. This is because these links do not have associated REPLACE operations.

\begin{definition}[RationalGRL Model]
\label{def:rationalgrl-model}
A \emph{RationalGRL model} $RationalGRL=(\overline{IE}, \overline{Act}, R_{ActIE}, \overline{Contrib}, Decomp, Dep, Arg, Att, Label)$ consists of:
\begin{itemize}
\item A set $\overline{IE}$ of lists of intentional elements (Def.~\ref{def:element-list}),
\item A set $\overline{Act}$ of lists of actors (Def.~\ref{def:element-list}),
\item A set $R_{ActIE}$ of Actor-IE relations (Def.~\ref{def:act-ie-relation}),
\item A set $\overline{Contr}$ of lists of contribution links (Def.~\ref{def:element-list}),
\item A set $Decomp$ of decomposition links (Def.~\ref{def:link:decomp}),
\item A set $Dep$ of dependency links (Def.~\ref{def:link:dependency}).
\item A set of generic arguments $Arg$ (Def.~\ref{def:generic-argument}),
\item A set of attack links (Def.~\ref{def:link:attack}).
\item A labeling function $Lab$ (Def.~\ref{def:labeling}).
\end{itemize}

Furthermore, the following conditions are satisfied. In the following, let $Elems = \{IE, Act, Contr, Decomp, Dep, Arg\}$:
\begin{enumerate}
\item ids are globally unique across IEs, Links, and Actors, i.e., let $X,Y\in \{\overline{IE},\overline{Act}, \overline{Contr}, Decomp, Dep\}$. For all $X_i$ and $Y_j$: if $i=j$ then $X=Y$ and $X_i=Y_j$.
\item All intentional elements of actors exist: $\forall (i,j)\in R_{ActIE}: \overline{act}_i \in \overline{Act} \wedge ie_j \in IE$.
\item An intentional element belongs at most to one actor: $\forall ie_i\in IE: |\{(k,i)\in R_{ActIE}\}| \le 1$.
\item Contribution links connect intentional elements: $\forall (i,j,k,value)\in \overline{Contrib}: \{ie_j,ie_k\}\subseteq IE$.
\item Decomposition links connect intentional elements: $\forall (i,j,k)\in Decomp: \{ie_j,ie_k\}\subseteq IE$.
\item Dependency links connect intentional elements: $\forall (i,j,)\in Dep: \{ie_j,ie_k\}\subseteq IE$.
\item Attack links connect generic arguments, IEs, actors, and links with each other, i.e., let   $\forall (i,j)\in Att: \exists X\in Elems$ s.t. $X_i\in X$ and $\exists Y\in Elems$ s.t. $Y_i\in Y$.
\end{enumerate}
\end{definition}

\subsubsection{Argumentation semantics}

In order to determine which arguments are accepted or not, we define \emph{argumentation semantics}. We used the standard approach here, which is known as \emph{Dung's semantics}. The following notions are preliminary.

\begin{definition}[Attack, conflict-freeness, defense, and admissibility~\cite{Dung1995}] Suppose an argumentation framework $AF=(Arg,Att)$, two sets of arguments $S\cup S'\subseteq Arg$, and some argument $A\in Arg$. We say that
\begin{itemize}
\item $S$ \emph{attacks} $A$ if some argument in $S$ attacks $A$,
\item $S$ \emph{attacks} $S'$ if some argument in $S$ attacks some argument in $S'$,
\item $S$ is \emph{conflict-free} if it does not attack itself,
\item $S$ \emph{defends} $A$ if for each $B$ such that $B$ attacks $A$, $S$ attacks $B$,
\item $S$ is \emph{admissible} if $S$ is conflict-free and defends each argument in it.
\end{itemize}
\end{definition}

@@

\begin{definition}[Preferred semantics~\cite{Dung1995}] \label{def:semantics}
A preferred extension of an argumentation framework $AF$ is a maximal (w.r.t. set inclusion) admissible set of $AF$.
\end{definition}

@@

\begin{algorithm}[h]
  \caption{Translation Algorithm}\label{alg:translation}
  \begin{algorithmic}[1]
    \State TODO
  \end{algorithmic}
\end{algorithm}

\begin{theorem}
If a RationalGRL model $m$ satisfies the conditions of a RationalGRL model (Def.~\ref{def:rationalgrl-model}), then $Trans(m)$ satisfies the conditions of a GRL model (Def.~\ref{def:grl-model}).
\end{theorem}

\begin{proof}
TODO
\end{proof}

>>>>

\subsection{Formal Specification of GRL}
\label{sect:formalframework:grl}

@@

\begin{definition}[General definitions]
\label{def:set-definitions}
Throughout this section, we adopt the convention that variables start with a lowercase letter (e.g, $id, i, j, name, ie, goal$), and sets and constants start with an uppercase letter (e.g., $Type, AND, Goal$).

We define the following sets:
\begin{itemize}
\item $Type = \{Softgoal, Goal, Task, Resource\}$,
\item $Names$ is a finite set of strings.
\item $DecompType = \{AND,OR,XOR\}$.
\item $ContribValue = \{Break, Hurt, Some\ nega-$ $tive, Unknown, Some\  positive, Help, Make\},$
\end{itemize}
\end{definition}

@@

\begin{definition}[Notation]
\label{def:notation}
We adopt three conventions simplifying our notation:
\begin{itemize}
\item
We refer to the element of an intention element $ie$ using the dot (".") notation. That is, we may refer to the id, type, name and decomposition type with respectively $ie.id$, $ie.type$, $ie.name$, and $ie.decomptype$.
\item 
We refer to the set of intentional elements with $ie.id=i$ by $IE_i$, and if this is a single element, we denote it by $ie_i$\footnote{In GRL, there always exists at most one element for every id (see Def.~\ref{def:grl-model}), in RationalGRL, however, this condition does not hold (see Def.~\ref{def:rationalgrl-model}).} For instance, we may refer to the intentional element $ie = (0, Goal, \text{Make profit}, AND)$ with $ie_0$ and write $ie_0.type = Goal$, $ie_0.name = \text{Make profit}$, and $ie_0.decompositiontype = AND$. 
\item
We can also refer to intention elements of a specific type simply by $type_{id}$. For instance, we can abbreviate the element in the previous item with $goal_0$ and write $goal_0.name = \text{Make profit}$, and $goal_0.decomptype = AND$.
\end{itemize}
\end{definition}

\begin{definition}[Actor]
\label{def:actor}
An actor $act \in \mathbb{N}\times Names$ is a relation where $act=(id,name)$ means:
\begin{itemize}
\item $id\in\mathbb{N}$ is the identifier of the actor, 
\item $name\in Names$ is a string description of its name.
\end{itemize}

@@

\begin{definition}[Contribution Link]
\label{def:link:contrib}
A \emph{contribution} link: $contrib\in \mathbb{N}\times\mathbb{N}\times\mathbb{N}\times Contribvalue$ is a relation such that $contrib = (i,j,k,value)$ means
\begin{itemize}
\item $i\in \mathbb{N}$ is the unique identifier of the link,
\item $j\in \mathbb{N}$ is the unique identifier of the IE from which the contribution originates,
\item $k\in \mathbb{N}$ is the unique identifier of the IE to which is contributed.
\end{itemize}
Intuitively, $contrib = (i,j,k,value)$ means that $ie_i$ contributes to $ie_j$ with $value$.

@@

\begin{definition}[Decomposition Link]
\label{def:link:decomp}
A \emph{decomposition} link: $decomp\in \mathbb{N}\times\mathbb{N}\times\mathbb{N}$ is a relation such that $decomp = (i,j,k)$ means
\begin{itemize}
\item $i\in \mathbb{N}$ is the unique identifier of the link,
\item $j\in \mathbb{N}$ is the unique identifier of the decomposing IE,
\item $k\in \mathbb{N}$ is the unique identifier of the IE that is being decomposed.
\end{itemize}
Intuitively, $decomp = (i,j,k)$ means that $ie_i$ decomposes $ie_j$.\footnote{Note that the decomposition type is defined on $IE_{k}$, see Definition~\ref{def:ie}.}

@@

\begin{definition}[Dependency Link]
\label{def:link:dependency}
A \emph{dependency} link: $dep\in \mathbb{N}\times\mathbb{N}\times\mathbb{N}$ is a relation such that $dep = (i,j,k)$ means
\begin{itemize}
\item $i\in \mathbb{N}$ is the unique identifier of the link,
\item $j\in \mathbb{N}$ is the unique identifier of the dependee IE,
\item $k\in \mathbb{N}$ is the unique identifier of the dependent IE.
\end{itemize}
Intuitively, $dep = (i,j,k)$ means that $ie_j$ depends on $ie_j$. \todo{Marc}{Sepideh}{Is this correct? For a dependency relation $A\rightarrow B$, who is dependent on who?}

@@

\begin{definition}[GRL Model]
\label{def:grl-model}
A \emph{GRL model} $GRL=(IE, Act, R_{ActIE}, Contr, Decomp, Dep)$ consists of:
\begin{itemize}
\item A set $IE$ of intentional elements (Def.~\ref{def:ie}),
\item A set $Act$ of actors (Def.~\ref{def:actor}),
\item A set $R_{ActIE}$ of Actor-IE relations (Def.~\ref{def:act-ie-relation}),
\item A set $Contr$ of contribution links (Def.~\ref{def:link:contrib}),
\item A set $Decomp$ of decomposition links (Def.~\ref{def:link:decomp}),
\item A set $Dep$ of dependency links (Def.~\ref{def:link:dependency}).
\end{itemize}
\end{definition}

@@

\begin{definition}[Valid GRL Model]
\label{def:valid-grl-model}
A GRL model $GRL=(IE, Act, R_{ActIE}, Contr, Decomp, Dep)$ (Def.~\ref{def:grl-model}) is a \emph{valid GRL model} iff the following conditions are satisfied:
\begin{enumerate}
\item ids are globally unique across IEs, Links, and Actors, i.e., let $X,Y\in \{IE,Act, Contr, Decomp, Dep\}$. For all $X_i$ and $Y_j$: if $i=j$ then $X=Y$ and $X_i=Y_j$.
\item All intentional elements of actors exist: $\forall (i,j)\in R_{ActIE}: act_i \in Act \wedge ie_j \in IE$.
\item An intentional element belongs at most to one actor: $\forall ie_i\in IE: |\{(k,i)\in R_{ActIE}\}| \le 1$.
\item Contribution links connect intentional elements: $\forall (i,j,k,value)\in Contrib: \{ie_j,ie_k\}\subseteq IE$.
\item Decomposition links connect intentional elements: $\forall (i,j,k)\in Decomp: \{ie_j,ie_k\}\subseteq IE$.
\item Dependency links connect intentional elements: $\forall (i,j,)\in Dep: \{ie_j,ie_k\}\subseteq IE$.
\end{enumerate}
\end{definition}

@@

\subsection{Formal specification of RationalGRL}
\label{sect:formalframework:rationalgrl}

In order to develop a logical framework for RationalGRL, we extend the GRL logical framework of the previous section by adding three elements (see Figure~\ref{fig:rationalgrllegend}):
\begin{itemize}
\item A new element called \emph{generic argument},
\item A new link called \emph{attack link}
\end{itemize}

Following the RationalGRL metamodel (Figure~\ref{fig:metamodel}), we define an \emph{Argument} as either a generic argument or any of the GRL elements, and we define attack relations between arguments. Thus, a RationalGRL model is simply a set of arguments and attack relations. We use \emph{argumentation semantics} to compute extensions, which are sets of accepted arguments.

@@

\begin{definition}[Generic Argument]
\label{def:generic-argument}
A generic argument $ga \in \mathbb{N}\times Names$ is a relation such that $ga=(id, name)$ means
\begin{itemize}
\item $id\in \mathbb{N}$ is the identifier of the generic argument,
\item $name\in Names$ is a string description of its name.
\end{itemize}
We may refer to the argument with id $i$ simply with $arg_i$. A set of arguments is denoted by $GA$.
\end{definition}

@@

\begin{definition}[Attack Link]
\label{def:link:attack}
An attack link $att\in \mathbb{N}\times \mathbb{N}$ is a relation such that $att=(i,j)$ means:
\begin{itemize}
\item $i\in \mathbb{N}$ is the unique identifier of the element that is performing that attack,
\item $j\in \mathbb{N}$ is the unique identifier of the element that is being attacked.
\end{itemize}
Intuitively, $att=(i,j)$ means that element $i$ is attacking element $j$. A set of attack links is denoted by $Att$.
\end{definition}

Note that the previous definition did not put any constraint on which elements can be connected with attack links. This is what we make explicit in the definition of a valid RationalGRL model later.

Next we define an argument as either a generic argument or any of the GRL elements or links. This captures the specification in the RationalGRL metamodel (Fig.~\ref{fig:metamodel}) in which the class \textsf{Argument} is a superclass of \textsf{GenericArgument} and \textsf{GRLModelElement}, which again is a superclass of both \textsf{ElementLink} and \textsf{GRLLinkableElement}. A \textsf{GRLLinkableElement} is in turn a superclass of \textsf{Actor} and \textsf{IntentionalElement}. In sum, we define an argument simply as any one of the GRL elements or links, or a generic argument.

\begin{definition}[Argument]
\label{def:argument}
A set of arguments $Arg = IE\cup Act\cup R_{ActIE}\cup Contr\cup Decomp \cup Dep\cup GA$ consists of:
\begin{itemize}
\item a set of intentional elements $IE$ (Def.~\ref{def:ie}), 
\item a set of actors $Act$ (Def.~\ref{def:actor}),
\item a set of Actor-IE relations $R_{ActIE}$ (Def.~\ref{def:act-ie-relation}), 
\item a set of contribution links $Contr$ (Def.~\ref{def:link:contrib}), 
\item a set of decomposition links $Decomp$ (Def.~\ref{def:link:decomp}), 
\item a set of dependency links $Dep$ (Def.~\ref{def:link:dependency}), 
\item a set of a generic arguments $GA$ (Def.~\ref{def:generic-argument}).
\end{itemize}
\end{definition}

\begin{definition}[RationalGRL Model]
\label{def:rationalgrl-model}
A \emph{RationalGRL model} $RationalGRL=(Arg, Att)$ consists of a set of arguments $Args$ (Def.~\ref{def:argument}) and a set of attack links $Att$ (Def.~\ref{def:link:attack}).
\end{definition}

The definition of a RationalGRL model of above is very general, and does not put any constraints on the model. In order to define the notion of a \emph{valid} RationalGRL model (similar to that of a valid GRL model, Def.~\ref{def:valid-grl-model}), we should be able to determine precisely when an argument is accepted and when not. This is what we do using argumentation semantics.  We used the standard approach here, which is known as \emph{Dung's semantics}. The following notions are preliminary.

\begin{definition}[Attack, conflict-freeness, defense, and admissibility~\cite{Dung1995}] Suppose a RationalGRL model $\emph{RationalGRL=(Arg,Att)}$, two sets of arguments $S\cup S'\subseteq Arg$, and some argument $A\in Arg$. We say that
\begin{itemize}
\item $S$ \emph{attacks} $A$ if some argument in $S$ attacks $A$,
\item $S$ \emph{attacks} $S'$ if some argument in $S$ attacks some argument in $S'$,
\item $S$ is \emph{conflict-free} if it does not attack itself,
\item $S$ \emph{defends} $A$ if for each $B$ such that $B$ attacks $A$, $S$ attacks $B$,
\item $S$ is \emph{admissible} if $S$ is conflict-free and defends each argument in it.
\end{itemize}
\end{definition}

@@

\begin{definition}[Preferred semantics~\cite{Dung1995}] \label{def:semantics}
A preferred extension of a RationalGRL model $R$ is a maximal (w.r.t. set inclusion) admissible set of $R$.
\end{definition}

@@

The previous definition of a preferred extension allows us to compute accepted arguments in a RationalGRL model. However, it does not yet put constraints on the resulting accepted arguments, and thus does not allow us to transform it into a valid GRL model. This is what we do in the following definition.

\begin{definition}[Valid RationalGRL Model]
A RationalGRL model \emph{R = $(Arg, Att)$} is a \emph {valid RationalGRL model} iff the preferred extension $E = IE\cup Act\cup R_{ActIE}\cup Contr\cup Decomp \cup Dep\cup GA$ forms a valid GRL model $(IE,  Act, R_{ActIE}, Contr, Decomp, Dep)$
\end{definition}
